---
title: "focd_analysis"
output: html_document
---

```{r}
library(tidyverse)
library(haven)
library(readxl)
library(ggplot2)
library(ggthemes)
library(stargazer)
```

```{r}
anes <- read_excel("ANES_2.xlsx") #ANES
anes_nov3 <- read_excel("ANES_geoNov3.xlsx") #Google Trends
kff <- read_excel("KFF_Vars3.xlsx") #Kaiser Family Foundation
```

```{r}
anes1 <- anes %>% group_by(statename) %>% 
  summarise(mean(V202329), 
  mean(V202330), 
  mean(V202331x), 
  mean(V202381), 
  mean(V202382))
```

Merging of Data
```{r}
anes_j_nov3 <- left_join(anes1, anes_nov3, by = "statename")
full_nov3 <- left_join(anes_j_nov3, kff, by = "statename")
```

Normalization
```{r}
min_max_norm <- function(x) {
    (x - min(x)) / (max(x) - min(x))
}

full_nov3_norm <- as.data.frame(lapply(full_nov3[2:15], min_max_norm))
full_nov3_norm$statename <- full_nov3$statename
full_nov3_norm$govparty <- full_nov3$govparty
full_nov3_norm$mask_oct_19_2020 <- full_nov3$mask_oct_19_2020

full_nov3_norm <- full_nov3_norm %>% 
  mutate(full_nov3_norm, repgov = ifelse(govparty == 'Republican', 1, 0))
full_nov3_norm <- full_nov3_norm[-c(51),]
```

Model 1 with norm_bg: not significant
```{r}
model1_bg = lm(mean.V202331x. ~ norm_bg + casepermil + deathpermil + pop + repgov, data = full_nov3_norm)
summary(model1_bg)
```

Model 1 with norm_5g: not significant
```{r}
model1_5g = lm(mean.V202331x. ~ norm_5g + casepermil + deathpermil + pop + repgov, data = full_nov3_norm)
summary(model1_5g)
```

Model 1 with norm_ch: not significant
```{r}
model1_ch= lm(mean.V202331x. ~ norm_ch + casepermil + deathpermil + pop + repgov, data = full_nov3_norm)
summary(model1_ch)
```

Model 1 with aggregate: not significant
```{r}
full_nov3_norm$norm_agg <- full_nov3_norm$norm_bg + full_nov3_norm$norm_5g + full_nov3_norm$norm_ch
model1_agg = lm(mean.V202331x. ~ norm_agg + casepermil + deathpermil + pop + repgov, data = full_nov3_norm)
summary(model1_agg)
```

Moderation Model with norm_bg: No moderation effect
```{r}
full_nov3_norm$int_bg <- full_nov3_norm$mask_oct_19_2020*full_nov3_norm$norm_bg
model2_bg = lm(mean.V202331x. ~ norm_bg + int_bg + mask_oct_19_2020 + casepermil + deathpermil + pop + repgov, data = full_nov3_norm)
summary(model2_bg)
```

Moderation Model with norm_5g: Moderation effect
```{r}
full_nov3_norm$int_5g <- full_nov3_norm$mask_oct_19_2020*full_nov3_norm$norm_5g
model2_5g = lm(mean.V202331x. ~ norm_5g + int_5g + mask_oct_19_2020 + casepermil + deathpermil + pop + repgov, data = full_nov3_norm)
summary(model2_5g)
```

Moderation Model with norm_ch: No moderation effect
```{r}
full_nov3_norm$int_ch <- full_nov3_norm$mask_oct_19_2020*full_nov3_norm$norm_ch
model2_ch = lm(mean.V202331x. ~ norm_ch + int_ch + mask_oct_19_2020 + casepermil + deathpermil + pop + repgov, data = full_nov3_norm)
summary(model2_ch)
```

Moderation Model with norm_agg: No moderation effect
```{r}
full_nov3_norm$int_agg <- full_nov3_norm$mask_oct_19_2020*full_nov3_norm$norm_agg
model2_agg = lm(mean.V202331x. ~ norm_agg + int_agg + mask_oct_19_2020 + casepermil + deathpermil + pop + repgov, data = full_nov3_norm)
summary(model2_agg)
```



5G and Aggregate Plots - OLS and Moderation Models
```{r}
#OLS 5g Plot
ns5g <- ggplot(full_nov3_norm, aes(x = norm_5g, y = mean.V202331x.)) + geom_point() + 
  geom_smooth(method='lm') + xlab("5G Conspiracy Google Trends") + ylab("Vaccine Hesitancy") + theme_light(base_size = 13)
ns5g

#Moderation 5g Plot
s5g <- ggplot(full_nov3_norm, aes(x = norm_5g, y = mean.V202331x., colour = as.factor(mask_oct_19_2020))) + geom_point() + 
  geom_smooth(method='lm', aes(group = mask_oct_19_2020), se = FALSE) + labs(x = "5G Conspiracy Google Trends") + labs(y = "Vaccine Hesitancy") + labs(colour = "Mask Mandate") + theme_light(base_size = 13)
s5g


#OLS Agg Plot
ols_agg_plot <- ggplot(full_nov3_norm, aes(x = norm_agg, y = mean.V202331x.)) + geom_point() + geom_smooth(method = 'lm') + xlab("Aggregate Conspiracy Google Trends") + ylab("Vaccine Hesitancy") + theme_light(base_size = 13)
ols_agg_plot

#Moderation Agg Plot
mod_agg_plot <- ggplot(full_nov3_norm, aes(x = norm_agg, y = mean.V202331x., colour = as.factor(mask_oct_19_2020))) + geom_point() + 
  geom_smooth(method='lm', aes(group = mask_oct_19_2020), se = FALSE) + xlab("Aggregate Conspiracy Google Trends") + ylab("Vaccine Hesitancy") + labs(colour = "Mask Mandate") + theme_light(base_size = 13)
mod_agg_plot

```




Stargazer plots for presentation
```{r}
#5g Models
stargazer(model1_5g, model2_5g, align=TRUE, 
          title="Effect of 5G Conspiracy Belief", data=full_nov3_norm,
          type="latex", style="ajps", out="focd_1.html", 
          dep.var.labels = "Vaccine Hesitancy",
          omit.stat = c("res.dev", "f", "adj.rsq"),
          covariate.labels=c("5G Conspiracy", "5G * Mask Mandate", "Mask Mandate", 
                             "Cases per mil.", "Deaths per mil.", "Population",
                             "Republican Governor"))

#Aggregate term models
stargazer(model1_agg, model2_agg, align=TRUE, 
          title="Effect of Aggregate Conspiracy Belief", data=full_nov3_norm,
          type="latex", style="ajps", out="focd_agg.html", 
          dep.var.labels = "Vaccine Hesitancy",
          omit.stat = c("res.dev", "f", "adj.rsq"),
          covariate.labels=c("Aggregate Conspiracy", "Agg. Conspiracy * Mask Mandate", "Mask Mandate", "Cases per mil.", "Deaths per mil.", "Population",
                             "Republican Governor"))
```

